---
title: "Example"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This package conducts mediator selection while controlling for false discovery rate (FDR).

```{r setup, message=FALSE,warning=FALSE}
library(MediationFDR)
```


## Data generation

Example data (exposure X, outcome Y, and potential mediators M) was generated as follows. 

For each subject $i = 1, ..., n$:

* $X_i \stackrel{i.i.d}{\sim} Bernoulli(prob = 0.5)$
* $M_{i,k} = \alpha_k X_i + e_{1_{i,k}}$, where $e_{1_{i,k}} \stackrel{i.i.d}{\sim} N(0, \Sigma), k = 1, ..., p, \Sigma$ is the variance-covariance matrix with diagonal entries 1 and off-diagonal entries $\rho$
* $Y_i = X_i + \sum_k b_{k} M_{i,k} + e_{2_{i}}$, where $e_{2_{i}} \stackrel{i.i.d}{\sim} N(0, 1)$

The 6th-15th M variables (M6,M7,M8,M9,M10,M11,M12,M13,M14,M15) are set to be the true mediators (i.e., having non-zero alpha and beta coefficients).

Specifically, the first 15 coefficients of alpha are set to take some non-zero value a, the 6th to 20th coefficients of beta are set to take some non-zero value b, and all other alpha and beta coefficients are set to be 0.

```{r}
## data generation
set.seed(20205)
data = datagen(n = 1000, p = 100, a = 0.5, b = 0.3, rho = 0.1)
```

## Mediator selection

```{r}
MediationFDR(X = data$X, Y = data$Y, M = data$M, V1 = NULL, V2 = NULL, q1 = 0.025, q2 = 0.025, f_func = "Diff", correction_method = "holm", weighted = FALSE)
```




